Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

Stack memory is used to store all objects that are actively in use or will be used in the near future. Heap memory is used to store all objects whose scope is unknown to the program. Memory management is the term used to describe heap memory management. When developers write programs that creates the objects in heap memory and deletes explicitly the objects when it is no longer in use is called manual memory management.

>>>>

Stack memory is used to store all objects that are actively in use or will be used in the near future. Heap memory is used to store all objects whose scope is unknown to the program. Memory management is the term used to describe management of heap. When developers explicitly delete objects when it is no longer in use is called manual memory management.
